---
title: "Online Resource 1"
output:
  html_document:
    highlight: haddock
    theme: readable
    toc: yes
---
```{r echo=FALSE}
knitr::opts_chunk$set(comment = NA)
```

# Related article

Article title : Bird seasonal beta-diversity in the contiguous United States

Journal name : Journal of Ornithology

Author name : Charles A. Martin

Affiliation : Université du Québec à Trois-Rivières

E-mail address : charles.martin1@uqtr.ca

# Goal

This online resource acts as an additional result to *Bird seasonal beta-diversity in the contiguous United States*, exploring the gamma:alpha ratio, as it was an important contributor to differences in beta-diversity along species pool size changes in Kraft et al. (2011).

Gamma diversity is total number of species for a state in a 10-year period. Alpha diversity is the average number of species per week per state in a 10-year period.

Data source is the same as in the related article (eBird frequency histograms from 2006 to 2016).

# Data loading and preparation
```{r message=FALSE}
library(tidyverse)
db <- read_csv("../data/distances.csv") %>%
  filter(complete.cases(.)) %>% 
  select(alpha, gamma, latitude, location) %>% 
  gather(key = metric, value = diversity, alpha, gamma)
```

# Database excerpt
```{r}
db
```

# Graphical representation of the relationship
Compare with Fig. 1A in Kraft et al. 2011
```{r}
db %>%
  ggplot(aes(x = latitude, y = diversity, col = metric, shape = metric)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  theme_minimal() +
  labs(x = "Latitude", y = "Diversity") +
  scale_color_manual(values = c("alpha" = "tomato", "gamma" = "royalblue"))
```

# Comparing models with and without the slope difference
```{r}
m1 <- lm(diversity~latitude * metric, data = db)
m2 <- lm(diversity~latitude + metric, data = db)
AIC(m1,m2) # Lower AIC = better model, i.e. no slope difference

summary(m2)
```

# References
Kraft NJ, Comita LS, Chase JM, et al (2011) Disentangling the Drivers of Beta Diversity Along Latidunial and Elevational Gradients. Science (80) 333:1755–1758. doi: 10.1007/s13398-014-0173-7.2
